Model

### 2019-11-13 stats/kids_basic_me.Rmd
first draft prior model

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

ggsave("../graphs/me_by_item.png", width = 6, height = 3, scale = 1.2)
```

>>>>

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  #geom_smooth(method = "loess", se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

ggsave("../graphs/me_by_item.png", width = 5, height = 4, scale = 1.2)
```

### 2019-11-13 stats/kids_novelty.Rmd
first draft prior model

d <- read_csv("../data/novelty.csv")%>%
  mutate(subage = factor(subage))

@@

## sanity checks
d %>%
  group_by(experiment,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())%>%
  kable()

@@

ggsave("../graphs/novelty.png", width = 5, height = 3, scale = 1.2)
```

>>>>

d_spin <- read_csv("../data/novelty.csv")%>%
  mutate(subage = factor(subage))

@@

## sanity checks
d_spin %>%
  group_by(experiment,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())%>%
  kable()

@@

ggsave("../graphs/novelty.png", width = , height = 4, scale = 1.2)
```

### 2019-11-13 stats/model.Rmd
first draft prior model

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)

@@

data_comb_log
```

@@

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  packages = c("webppl_packages/webppl-sample-writer")
)

bind_rows(
sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
)

saveRDS(sem_know_model, "../saves/model_complete.rds")

sem_know_model <- readRDS("../saves/model_complete.rds")

@@

```{r}
log_like <- sem_know_model %>%
  filter(a == "log_like")%>%
  select(b,c,e)%>%
  rename(model = b, 
         parameter = c,
         log_like = e)

saveRDS(log_like, "../saves/log_like.rds")
log_like <- readRDS("../saves/log_like.rds")

@@

saveRDS(log_like_model, "../saves/log_like_model.rds")
log_like_model <- readRDS("../saves/log_like_model.rds")

@@

saveRDS(log_like_chain, "../saves/log_like_chain.rds")
log_like_chain <- readRDS("../saves/log_like_chain.rds")

log_like_chain %>%
  group_by(model)%>%
  mutate(noise = round(noise,2),
         parameter_free = round(parameter_free,2))%>%
  summarise(range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
```

@@

model_params<- sem_know_model %>%
  filter(a == "parameter")

saveRDS(model_params, "../saves/model_params.rds")
model_params <- readRDS("../saves/model_params.rds")

@@

saveRDS(item_params, "../saves/item_params.rds")
item_params <- readRDS("../saves/item_params.rds")

@@

saveRDS(global_params, "../saves/global_params.rds")
global_params <- readRDS("../saves/global_params.rds")

global_sigma<- sem_know_model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

saveRDS(global_sigma, "../saves/global_sigma.rds")
global_sigma <- readRDS("../saves/global_sigma.rds")

@@

@@

plot_model_pred <- model_pred%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(model + alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

## Correlate model predictions

@@

cor_model_pred <- model_pred%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(model = "globalPrag_free"),
      binnned_data%>%mutate(model = "globalPrag_noise"),
      binnned_data%>%mutate(model = "pragmatic_free"),
      binnned_data%>%mutate(model = "pragmatic_noise")
      )
  )

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 1,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

@@

@@

```{r}
ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_wrap(~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

@@

```{r}
noise_plot <- bind_rows(
  prag_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Pragmatic"),
  global_prag_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Pragmatic no word knowledge"),
  flat_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Flat Prior"),
  prior_only_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Prior Only")
)

ggplot(noise_plot, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .7)+
  theme_few()+
  xlim(0,1)+
  scale_color_ptol()+
  scale_fill_ptol()+
  theme(legend.position = "bottom")

@@

@@

```{r}
binned_noise_model <- prag_model_noise %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         subage = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(subage, alignment, item)%>%
  summarise(model_mean = estimate_mode(value),
            model_ci_lower = hdi_lower(value),
            model_ci_upper = hdi_upper(value))

@@

ggplot(data = cor_plot_2,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

>>>>

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

@@

@@

### Prior model

```{r}
prior_params <- '

var priorData = dataFromR.data

var subjects = levels(priorData, "subid")

//display(subjects)

  var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})

  var subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})

  var sampleSub = function(age){
    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
  }

  foreach(function(subid){
      var subjectData = _.filter(priorData, {subid: subid})

      display(subjects)

      var subj_age = subjectData[0].age
      var subjectPrior = sampleSub(subj_age)

      var priorReg = logistic(prior_int + prior_slope * subjectPrior)

      var prior = [priorReg, 1-priorReg]

  query.add(["intercept"], [prior_int])
  query.add(["slope"], [prior_slope])
  query.add(["sigma"], [subject_sigma])

  return query

}

prior_data <- read_csv("../data/novelty.csv")%>%
  mutate(age = age_num - min(age_num))

prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
  data = list(data = prior_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 10000, burn = 5000, verbose = T)
)

prior <- prior_model%>%
  mutate(value = unlist(value))%>%
  filter(Chain !=2)

prior_summary <- prior%>%
  group_by(Parameter)%>%
  summarise(param_map = estimate_mode(value))

```{r}
ggplot(prior, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(Parameter~., scales = 'free')+
  theme_few()

```{r}
novel_bm <- readRDS("../saves/novelty_model.rds")
summary(novel_bm)
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 2,
  cores = 2,
  packages = c("webppl_packages/webppl-sample-writer")
)

@@

```{r}
log_like <- bind_rows(
  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
)

@@

@@

log_like_chain %>%
  group_by(model)%>%
  mutate(noise = round(noise,2),
         parameter_free = round(parameter_free,2))%>%
  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))

log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))

log_like_model_2 <- log_like_2%>%
  group_by(model,noise)%>%
  summarize(logP = logSumExp(log_like))

model_comp <- log_like_2%>%
  spread(model,log_like)%>%
  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
         prag_vs_flat_prior = pragmatics - flat_prior,
         prag_vs_prior_only = pragmatics - prior_only)%>%
  group_by(noise)%>%
  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
            prag_vs_prior_only = logSumExp(prag_vs_prior_only))

```{r}
ggplot(log_like_model, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  facet_grid(~parameter)+
  ylim(-1750,-1150)+
  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
    theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())
```

```{r}
ggsave("../graphs/like.png", width = 6, height = 2.5, scale = 1.5)
```

@@

model_params <- bind_rows(
  readRDS("../saves/model_params_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_params_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/model_params_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/model_params_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/model_params_chain5.rds")%>%mutate(chain = 5)

)

@@

@@

global_sigma<- model_params %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

@@

### Pragmatic free model

```{r}
data_comb_plot<-data_comb%>%
  mutate(model = "data")

model_pred_prag_free<- bind_rows(
  readRDS("../saves/model_pred_pragmatic_free_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_pred_pragmatic_free_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/model_pred_pragmatic_free_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/model_pred_pragmatic_free_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/model_pred_pragmatic_free_chain5.rds")%>%mutate(chain = 5)
)

plot_model_pred_prag_free <- model_pred_prag_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_prag_free, "../saves/plot_model_pred_prag_free.rds")
plot_model_pred_prag_free <- readRDS("../saves/plot_model_pred_prag_free.rds")

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_prag_free, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred_prag_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

x <- sample(1:48000, 500)

plot_model_prag_noise_line <- model_pred_prag_free%>%
  filter(iteration %in% x)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .05)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)
```

```{r}
ggsave("../graphs/pred_model_data.pdf", width = 10, height = 4, scale = 1)
```

### Pragmatic noise model

@@

model_pred_prag_noise<- bind_rows(
  readRDS("../saves/model_pred_pragmatic_noise_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_pred_pragmatic_noise_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/model_pred_pragmatic_noise_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/model_pred_pragmatic_noise_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/model_pred_pragmatic_noise_chain5.rds")%>%mutate(chain = 5)
)

plot_model_pred_prag_noise <- model_pred_prag_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_prag_noise, "../saves/plot_model_pred_prag_noise.rds")
plot_model_pred_prag_noise <- readRDS("../saves/plot_model_pred_prag_noise.rds")

plot_model_pred_prag_noise_chain <- model_pred_prag_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item,chain, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_prag_noise_chain, "../saves/plot_model_pred_prag_noise_chain.rds")
plot_model_pred_prag_noise_chain <- readRDS("../saves/plot_model_pred_prag_noise_chain.rds")

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_ribbon(data = plot_model_pred_prag_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .3) +
  geom_line(data = plot_model_pred_prag_noise, aes(x=age+2,y = mean, col = model), size = 1, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

x <- sample(1:48000, 500)

plot_model_prag_noise_line <- model_pred_prag_noise%>%
  filter(iteration %in% x)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .4, span = 2)+
  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .075)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)
```

```{r}
ggsave("../graphs/model_pred_noise_ribbon.pdf", width = 10, height = 4, scale = 1.2)
```

### Global pragmatic free model

model_pred_global_free<- bind_rows(
  readRDS("../saves/model_pred_globalPrag_free_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_pred_globalPrag_free_chain2.rds")%>%mutate(chain = 2)
)

plot_model_pred_global_free <- model_pred_global_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_global_free, "../saves/plot_model_pred_global_free.rds")
plot_model_pred_global_free <- readRDS("../saves/plot_model_pred_global_free.rds")

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_global_free, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred_global_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(model + alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

### Global pragmatic noise model

model_pred_global_noise<- bind_rows(
  readRDS("../saves/model_pred_globalPrag_noise_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_pred_globalPrag_noise_chain2.rds")%>%mutate(chain = 2)
)

plot_model_pred_global_noise <- model_pred_global_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_global_noise, "../saves/plot_model_pred_global_noise.rds")
plot_model_pred_global_noise <- readRDS("../saves/plot_model_pred_global_noise.rds")

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_global_noise, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred_global_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(model + alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

@@

cor_prag_free <- model_pred_prag_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

saveRDS(cor_prag_free, "../saves/cor_prag_free.rds")
cor_prag_free <- readRDS( "../saves/cor_prag_free.rds")

cor_prag_noise <- model_pred_prag_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

saveRDS(cor_prag_noise, "../saves/cor_prag_noise.rds")
cor_prag_noise <- readRDS( "../saves/cor_prag_noise.rds")

cor_global_free <- model_pred_global_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_global_noise <- model_global_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  cor_prag_free,
  cor_prag_noise
 # cor_global_free,
#  cor_global_noise
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      #binnned_data%>%mutate(model = "globalPrag_free"),
      #binnned_data%>%mutate(model = "globalPrag_noise"),
      binnned_data%>%mutate(model = "pragmatic_free"),
      binnned_data%>%mutate(model = "pragmatic_noise")
      )
  )

saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 1.5, stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~age)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

```{r}
ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
```

@@

summary(novel_bm)

@@

```{r}
ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
geom_smooth(data = data_comb_plot, 
            aes(x = age_num, y = correct), 
            col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
  geom_pointrange(data = p1, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .6) +
  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_wrap(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

p1 <- data_comb%>%
  mutate(alignment = condition)%>%
  group_by(alignment, item ,subage)%>%
  multi_boot_standard(col = "correct")

ggplot(p1, aes(x = subage, y = mean))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))+
  facet_grid(condition ~familiarObject)+
  geom_line(aes(group=condition))+
  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .5) +
  theme_few() +

@@

```{r}
noise_plot <- bind_rows(
  prag_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Pragmatic"),
  global_prag_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Pragmatic global"),
  flat_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Flat Prior"),
  prior_only_model_noise %>%
    filter(Parameter %in% c("noise"))%>%
    mutate(Model = "Prior Only")
)

ggplot(noise_plot, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .7, bw = .01)+
  theme_few()+
  xlim(0,1)+
  scale_color_ptol()+
  scale_fill_ptol()+
  theme()

@@

```{r}
ggsave("../graphs/noise.pdf", width = 6, height = 3, scale = 1.2)
```

@@

```{r}
binned_noise_model <- prag_model_noise %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         subage = factor(cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4))))%>%
  group_by(subage, alignment, item)%>%
  summarise(model_mean = estimate_mode(value),
            model_ci_lower = hdi_lower(value),
            model_ci_upper = hdi_upper(value))

@@

ggplot(data = cor_plot_2,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

```{r}
ggsave("../graphs/cor_plot_noise.pdf", width = 10, height = 4, scale = .8)
```
